DRAFT \\ From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics

### 2017-01-19 2015CompleteDerivation/completeDerivation.tex
Added acknowledgement section fixed appendix format

\section{Appendix: mathematical proofs}

>>>>

\begin{acknowledgements}
We'd like to thank Erik Curiel, Jiahua Gu, Josh Hunt, Isaac Mooney and Pavel Okun for providing feedback on drafts of this manuscript, Mark Greenfield for further insights in the topological aspects and Alan Phillips for contributing figures. We additionally thank Paul Stankus for interest and support in the earlier stages of this project. Funding for this work was provided in part by the MCubed program of the University of Michigan.
\end{acknowledgements}

\appendix
\section*{Appendix A. Mathematical proofs}
\stepcounter{section}
